---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gqrf

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/gqrf)](https://CRAN.R-project.org/package=gqrf)
<!-- badges: end -->

'gqrf' is an R package for implementing geographic quantile regression forest method for spatial interpolation as described in Maxwell et al, (2020).

## Installation

You can install the released version of project from [CRAN](https://CRAN.R-project.org) with:

```{r,  message = FALSE, warning=FALSE}
#install.packages("gqrf")
```

And the development version from [GitHub](https://github.com/) with:

```{r, message = FALSE, warning=FALSE}
# install.packages("devtools")
devtools::install_github("Gitmaxwell/gqrf")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r}
#library(gqrf)
## basic example code

```

## References

Maxwell, K., Rajabi, M., Esterle, J. (2020). Spatial interpolation of coal geochemical properties using geographic quantile regression forest. Manuscript submitted for publication.

